Yaourt pliss\'{e}, yaourt flamb\'{e}

### 2014-04-07 plis_figures.tex
zoom with nodes

		\draw[Accent2] (a.north west) ++(0.111\columnwidth, -0.072\columnwidth) rectangle +(0.137\columnwidth,-0.137\columnwidth) -- (b.south west) (a.north west) ++(0.248\columnwidth, -0.072\columnwidth) -- (b.north west);
		\draw[Main] (b.north west) ++(0.097\columnwidth,-0.143\columnwidth) rectangle +(0.128\columnwidth,-0.081\columnwidth) -- (c.south west) (b.north west) ++(0.225\columnwidth,-0.143\columnwidth) --(c.north west);
		\draw[Accent1] (c.north west) ++(0.125\columnwidth,0) rectangle +(0.156\columnwidth,-0.156\columnwidth);

>>>>

		\node[minimum width = 0.137\columnwidth, minimum height=0.137\columnwidth, anchor=north west, draw=Accent2] at ($(a.north west) +(0.111\columnwidth,-0.072\columnwidth)$) (bz){};
		\draw[Accent2] (bz.north east) -- (b.north west) (bz.south east) -- (b.south west);
		\node[minimum width = 0.128\columnwidth, minimum height=0.081\columnwidth, anchor=north west, draw=Main] at ($(b.north west) +(0.097\columnwidth,-0.143\columnwidth)$) (cz){};
		\draw[Main] (cz.north east) -- (c.north west) (cz.south east) -- (c.south west);
		\node[minimum width = 0.156\columnwidth, minimum height=0.156\columnwidth, anchor=north west, draw=Accent1] at ($(c.north west) + (0.125\columnwidth,0)$) (dz) {};
